---
title: "Layout Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{layout-options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(ggflowchart)
```

Create a tibble (or data frame) with each row representing an edge.

```{r data}
data <- tibble::tribble(
  ~from, ~to,
  "A", "B",
  "B", "C"
)
```

The default layout option, `"tree"` uses the tree layout from {igraph}.

```{r tree}
ggflowchart(data, layout = "tree")
```

If you want more control over where the nodes are positioned, you can specify `layout = "custom"`. If you choose this option, you **must** have a column named `x` and a column named `y` in `node_data` (alongside `name`) specifying the coordinates of the centre of each node.

```{r custom}
node_data <- tibble::tribble(
  ~name, ~x, ~y,
  "A", 1, 3,
  "B", 2, 2,
  "C", 3, 1
)
ggflowchart(data, node_data = node_data, layout = "custom")
```

This means you can also create layouts using other functions or packages. For example, you could create a custom layout using `igraph::layout_nicely()` and pass it into `node_data`:

```{r igraph}
library(dplyr)
# generate edges
data <- tibble::tibble(
  from = LETTERS[1:4],
  to = LETTERS[2:5]
  )
# use a different layout from {igraph}
g <- igraph::graph_from_data_frame(
  select(data, c(from, to)),
  directed = TRUE)
coords <- igraph::layout_nicely(g)
colnames(coords) <- c("x", "y")
node_data <- tibble::as_tibble(coords) %>%
  mutate(name = igraph::vertex_attr(g, "name"))
# create flowchart
ggflowchart(data, node_data = node_data, layout = "custom")
```

Some of these alternative layouts (especially ones from {igraph}), may eventually become additional layout options within {ggflowchart}. Note that the placement of the arrows may work better with some layout options than others.
