---
title: "Styling Flowchart Nodes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{style-nodes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(ggflowchart)
```

Create a tibble (or data frame) with each row representing an edge.

```{r data}
data <- tibble::tribble(
  ~from, ~to,
  "A", "B",
  "B", "C"
)
```

Vary the widths of the nodes by adding a column called `x_nudge` to the `node_data`:

```{r node-width}
node_data <- tibble::tribble(
  ~name, ~x_nudge,
  "A", 0.3,
  "B", 0.4,
  "C", 0.5
)
ggflowchart(data, node_data)
```

Similarly, the height of the boxes can vary by adding a column called `y_nudge`. If neither `x_nudge` or `y_nudge` columns are present in `node_data`, then the values specified in the `x_nudge` or `y_nudge` arguments of `ggflowchart()` are used for all boxes.

Vary the fill colours of the nodes by specifying a column in `node_data` to colour by:

```{r node-fill}
node_data <- tibble::tribble(
  ~name, ~type,
  "A", "Yes",
  "B", "Yes",
  "C", "No"
)
ggflowchart(data, node_data, fill = type)
```

You can use existing `scale_fill_*` functions to change the colours:

```{r node-fill-change}
ggflowchart(data, node_data, fill = type) +
  ggplot2::scale_fill_brewer(palette = "Dark2")
```

You can do something very similar to change the colour of the text in the nodes:

```{r node-text}
ggflowchart(data, node_data, text_colour = type) +
  ggplot2::theme(legend.position = "none")
```

You will soon also be able to change the shape of nodes - keep an eye on the development version for this feature!
